---
title: "Shiny Application and Reproducible Pitch"
author: "Nasim Ahmed"
date: "13 November 2018"
output: ioslides_presentation
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##Diamond Analysis Report
In this part, we will present diamond analysis report enabled developing data products using shiny apps being embedded within Rmarkdown



## Application Overview
- There are several parameters exist in diomonds products and which can be analysized to find out those  parameter.
- The common parameters are Carat, Price, sample, size, and color depth.
- In this report, we will try to find out the right parameters for the best Diamonds parameter.


## Data Used

The diamonds data set is used for this application, which is part of ggplot2 package. Containing information about 53940 diamonds with 10 variables.


```{r, echo=TRUE}
library(ggplot2)
head(diamonds)
```

## Shiny files
The application is build using shiny package and there are two source code files such as

ui.R and server.R

The above file can be found here : [https://github.com/nasim751/Course-Project-Shiny-Application-and-Reproducible-Pitch]
